A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-06-20 papers/contact/paper.tex
changed plotting and latex for contact Tested everything on node03.

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-10}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:gnn-walls-10}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-30}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:gnn-walls-30}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-40}
  \caption{Density and contact densities at a wall with bulk filling
    fraction of 0.1.}
  \label{fig:gnn-walls-10}
\end{figure}

@@

>>>>

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-10}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.1.}
  \label{fig:gnn-walls-10}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-30}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.3.}
  \label{fig:gnn-walls-30}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-walls-40}
  \caption{Correlation multiplied twice by density with bulk filling
    fraction of 0.4.}
  \label{fig:gnn-walls-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-sphere-08-013}
  \caption{Correlation multiplied twice by density of 13 hard spheres in a
    spherical cavity with diameter 8.}
  \label{fig:gnn-sphere-08-013}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-sphere-12-112}
  \caption{Correlation multiplied twice by density of 112 hard spheres in a
    spherical cavity with diameter 12.}
  \label{fig:gnn-sphere-12-112}
\end{figure}

\begin{figure}
  \includegraphics[height=9cm]{figs/gnn-sphere-16-265}
  \caption{Correlation multiplied twice by density of 265 hard spheres in a
    spherical cavity with diameter 16.}
  \label{fig:gnn-sphere-16-265}
\end{figure}
